Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-02 analysis/paper/hotspots-paper.Rmd
trying to fix call to pmap

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "7/27/2019"
bibliography: research.bib
linkReferences: true
link-citations: true
output: 
  - bookdown::html_document2:
    code_folding: hide
  - bookdown::pdf_document2:
    code_folding: hide  
---

@@

```{r setup_continued-2}
hot_chr <- 2
hot_mid <- 165.5
keller_mediator <- "Hnf4a"
```

```{r}
knitr::knit_expand(file = here::here("analysis", "paper", "hotspot-one-chromosome.Rmd"))
```

@@

@@

```{r setup_continued-5}
hot_chr <- 5
hot_mid <- 146
keller_mediator <- "Pdx1"
```

```{r child="hotspot-one-chromosome.Rmd"}
```

@@

```{r setup_continued-7}
hot_chr <- 7
hot_mid <- 46
keller_mediator <- "Fam83e"
```

```{r child="hotspot-one-chromosome.Rmd"}
```

@@

```{r setup_continued-11}
hot_chr <- 11
hot_mid <- 71
keller_mediator <- "Sat2"
```

```{r child="hotspot-one-chromosome.Rmd"}
```

@@

```{r setup_continued-13}
hot_chr <- 13
hot_mid <- 112.5
keller_mediator <- "Il6st"
```

```{r child="hotspot-one-chromosome.Rmd"}
```

>>>>

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "August 1, 2019"
bibliography: research.bib
linkReferences: true
link-citations: true 
output: 
  bookdown::html_document2:
    code_folding: hide
---

@@

```{r, load_purrr}
library(purrr)
```

```{r setup_continued}
hot_chr <- c(2, 5, 7, 11, 13)
hot_mid <- c(165.5, 146, 46, 71, 112.5)
keller_mediator <- c("Hnf4a", "Pdx1", "Fam83e", "Sat2", "Il6st")
out <- pmap(tibble(hot_chr, hot_mid, keller_mediator), .f = function(hot_chr, hot_mid, keller_mediator) knitr::knit_expand(text = readLines(here::here("analysis", "paper", "hotspot-one-chromosome.Rmd"))))
# note that ... argument must be a list, ie, it must be a single argument, not multiple args
```

@@

`r knitr::knit(text = out[[1]])`

@@

@@

@@

@@
